---
title: "CH3/40220"
subtitle: "Workshop: DNA binding"
author: "Fiona Dickinson"
date: "10/03/2022"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Course Timetable

- Week 1: <span style="color:lightgrey">In Person - Intro to the course, refresher course on thermodynamics</span>
- Week 2: <span style="color:lightgrey">LOIL - Lecture - Crown & lariat ethers and related molecules</span>
- Week 3: <span style="color:lightgrey">In Person - Workshop (research paper based exercise)</span>
- Week 4: <span style="color:lightgrey">LOIL - Lecture - Self assembly the basics, DNA duplexing and beyond</span>
- Week 5: <span style="color:crimson">In Person - Workshop (research paper based exercise) </span>
- Week 6: <span style="color:darkturquoise">LOIL - Lecture - Tertiary structures</span>
- Week 7: In Person - Workshop (research paper based exercise)
- Week 8: <span style="color:darkturquoise">LOIL - Lecture - Binding of small molecules to biopolymers</span>
- Week 9: In Person - Workshop (research paper based exercise)
- Week 10: <span style="color:darkturquoise">LOIL - Lecture - Solvation, hydrodynamics & osmosis</span>
- Week 11: In Person - Workshop example exam questions

## The workshop

[DNA nearest neighbour thermodynamics](http://libproxy.bath.ac.uk/login?url=https://www.pnas.org/doi/full/10.1073/pnas.95.4.1460)


## Workshop - 1



## Workshop - 2



## Workshop - 3
